Linked Open Social Data for Scientific Benchmarking

### 2016-07-13 paper.tex
added table about provenance

Big data.
\subsection{Data outline}
Relations only (Facebook), text only (AA, Cidade Democratica).
\input{misc/overallText}
\input{tables/nsnapshots}
\input{tables/basicOverall}
% stats:
%% number of triples
%% number of edges
%% number of chars
%% number of users
% diagrams
\subsection{Software tools}
% triplification routines
% analysis routines
% envisioned multimedia routines    
\subsection{SPARQL queries}\label{queries}
% all text from user
% users with the most friendships
% users with most interactions
% search string in messages

\section{Conclusions}
\label{conclusions}
The Linked Open Social Data (LOSD) presented in this article
should be available online in the \url{http://linkedopensocialdata.org}
address in near future to fulfill the purpose of being a common
repertoire in current research.

>>>>

Big data.
\subsection{Data outline}
Relations only (Facebook), text only (AA, Cidade Democratica).
\input{misc/overallText}
\input{tables/nsnapshots}
\input{tables/basicOverall}
% stats:
%% number of triples
%% number of edges
%% number of chars
%% number of users
% diagrams in the supporting information file
\subsection{Software tools}
The LOSD is released with a software for rendering itself, analyses and
multimedia artifacts.
\subsubsection{Triplification routines}
For each social platform there is a \emph{triplification} routine,
i.e. a script for translating data to RDF.
Original formats and further observations are presented in
Table~\ref{tab:provenance}.
\begin{table*}[h!]\scriptsize
\begin{center}
\caption{Social platforms, original formats and further observations for
the LOSD dataset.}
\begin{tabular}{| l || c | c |}\hline
    \textbf{social platform} & \textbf{original format} & \textbf{further observations} \\\hline\hline
    AA & MySQL and MongoDB databases; IRC text logs & donated by AA users \\\hline
    Cidade Democrática & MySQL database & donated by admins \\\hline
    Email & mbox & obtained through Gmane public database \\\hline
    Facebook & GDF, GML and TAB & obtained through Netvizz~\cite{netvizz} \\\hline
    IRC & plain text log & obtained through Supybot logging \\\hline
    ParticipaBR & PostgreSQL database & donated by admins \\\hline
    Twitter & Json & obtained through Twitter streaming API \\\hline
\end{tabular}\end{center}
\end{table*}                    
\subsubsection{Topological and textual Analysis}
\subsubsection{Multimedia rendering}
\subsection{SPARQL queries}\label{queries}
% all text from user
% users with the most friendships
% users with most interactions
% search string in messages

\section{Conclusions}
\label{conclusions}
The Linked Open Social Data (LOSD) presented in this article
should be available online in the \url{http://linkedopensocialdata.org}
address in near future to fulfill the purpose of being a common
repertoire in current research.
One should access \url{http://wiki.nosdigitais.teia.org.br/LOSD}
for reaching the address where LOSD is currently reachable.
